### 2023-03-30 reachable-resilience.tex
l'idée de la preuve ...

@@

\begin{theorem}
{\sc Reachable-resilience} is decidable for (not necessarily strong) WSTS with effective 
$\uparrow$ $\post^*$ basis.
\end{theorem}

>>>>

The idea behind the proof is the following. For deciding whether a downward-closed set $D$ is reachable from $s$, we check whether
$B_{\post^*(s)} \cap D = \emptyset$, equivalent to $\post^*(s)\cap D = \emptyset$ by
Lemma~\ref{Lemma intersection}. For the converse direction, we compute the sequence of upward-closed
$U_n = \uparrow post^{\leq n}(s)$ until it becomes stationnary. 
Decidability of downward reachability leads to the decidability of the following stop condition:
asking whether $S \setminus U_n$ is reachable from $s$.

@@

\begin{theorem}{(Adjusting Theorem 1 from \cite{DBLP:journals/corr/abs-2108-00889})}
{\sc Reachable-resilience} is decidable for (not necessarily strong) WSTS with effective 
$\uparrow$ $\post^*$ basis.
\end{theorem}
